\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2016-10-05 redaction/dhp_sept2016.tex
modif_test_JH

\title{\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}} %\thanks{We are especially grateful to XXX. Part of this research was funded by the French Agence Nationale de la Recherche (ANR), under grant ANR-11-JSH1 002 01. Finally, any remaining errors are ours.}}}
%We also thank participants at the EEA 27\textsuperscript{th} Congress (Oslo), ETSG 13\textsuperscript{th} meetings (Copenhagen), INFER Workshop (Orleans), 45\textsuperscript{th} Congress of the Canadian Economic Association (Ottawa), IAW Workshop (Tubingen), and seminars at WTO, Strathclyde University, OFCE and EQUIPPE-University of Lille.
\author{Guillaume \textsc{Daudin}\thanks{%
Universit\'{e} Paris-Dauphine, PSL Research University, LEDa-DIAL, UMR 225, France \&
SciencesPo, Observatoire Français des Conjonctures \'{E}conomiques (OFCE), France}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Universit\'{e} de Lille - LEM-CNRS UMR 9221, France \& CEPII, France}\qquad Lise \textsc{Patureau}\thanks{Universit\'{e} Paris-Dauphine, PSL Research University, LEDa, France } }

>>>>

\title{\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}} %\thanks{We are especially grateful to XXX. Part of this research was funded by the French Agence Nationale de la Recherche (ANR), under grant ANR-11-JSH1 002 01. Finally, any remaining errors are ours.}}}
%We also thank participants at the EEA 27\textsuperscript{th} Congress (Oslo), ETSG 13\textsuperscript{th} meetings (Copenhagen), INFER Workshop (Orleans), 45\textsuperscript{th} Congress of the Canadian Economic Association (Ottawa), IAW Workshop (Tubingen), and seminars at WTO, Strathclyde University, OFCE and EQUIPPE-University of Lille.
\author{Guillaume \textsc{Daudin}\thanks{%
Universit\'{e} Paris-Dauphine, PSL Research University, LEDa-DIAL, UMR 225, France \&
SciencesPo, Observatoire Français des Conjonctures \'{E}conomiques (OFCE), France}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Universit\'{e} de Lille - Sciences et Technologies, LEM-CNRS UMR 9221, France \& CEPII, France}\qquad Lise \textsc{Patureau}\thanks{Universit\'{e} Paris-Dauphine, PSL Research University, LEDa, France } }
